### 2022-05-16 manuscript.Rmd
Shorten sub-headings
Create separate reference sections

bibliography      : "manuscript_files/references.bib"
csl               : "manuscript_files/nature.csl"

@@

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"
output            : papaja::apa6_pdf
header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \DeclareCaptionLabelSeparator{bar}{ | }
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
---

@@

## Publication bias and certainty assessment

@@

@@

@@

```{r, fig4, include=TRUE, fig.width=6, fig.cap="(ref:fig4-caption)", out.width="50%"}
# Include the flowchart (which was created manually with MS PowerPoint)
knitr::include_graphics(here("manuscript_files/flowchart.pdf"))
```

@@

\newpage
\renewcommand{\arraystretch}{2}
\singlespacing
\scriptsize

@@

## Reporting bias and certainty assessment

@@

@@

<div id="refs"></div>

>>>>

bibliography_main    : "manuscript_files/main.bib"
bibliography_methods : "manuscript_files/methods.bib"
csl                  : "manuscript_files/nature.csl"
citeproc             : false
link-citations       : yes

@@

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"

output:
  papaja::apa6_pdf:
    pandoc_args: "--lua-filter=manuscript_files/multiple-bibliographies.lua"

header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \DeclareCaptionLabelSeparator{bar}{ | }
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{belowskip=20pt,font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
---

@@

## Publication bias assessment

@@

::: {#refs_main}
:::

@@

```{r, fig4, include=TRUE, fig.width=6, fig.cap="(ref:fig4-caption)", fig.pos="ht", out.width="50%"}
# Include the flowchart (which was created manually with MS PowerPoint)
knitr::include_graphics(here("manuscript_files/flowchart.pdf"))
```

@@

@@

\renewcommand{\arraystretch}{2}
\singlespacing
\scriptsize

@@

## Publication bias assessment

@@

# Methods references

@@

::: {#refs_methods}
:::
